---
title: "Research Products: HRSA/ACF D89MC23154"

---

***
***
# Overview

Project Duration: 2011-2015

> Evaluates MIECHV expansion and enhancement of Evidence-based Home Visitation programs in four Oklahoma counties.

This page contains the products from the 2011 funded proposal, [HRSA/ACF D89MC23154](https://perf-data.hrsa.gov/mchb/DGISReports/Abstract/AbstractDetails.aspx?Source=TVIS&GrantNo=D89MC23154&FY=2012): "OUHSC CCAN Independent Evaluation of the State of Oklahoma Competitive Maternal, Infant, and Early Childhood Home Visiting (MIECHV) Project." 

***
***
# Resources and Files
Understanding of this proposal may benefit from the following resources: 

 * [Expansion Program Logic Model](./funding/2011a/funding_2011a_logic_model.pdf)

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of just one directory.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
#   opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  fig.width = 6.5, 
  fig.height = 4, 
  fig.path = 'FigureRaw/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./r.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r LoadData, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r TweakData, echo=echoChunks, results='show', message=FALSE}
```

***
***
# Aims of the External Evaluation
#### Description
Oklahoma's Maternal, Infant, Early Childhood Home Visitation (MIECHV) Expansion project has two primary branches  of evaluation, the *internal* evaluation conducted by the Oklahoma State Dept. of Health (OSDH) and the *external* evaluation conducted by the OU Health Sciences Center, Center on Child Abuse and Neglect (CCAN).  This summary report describes the progress to date for the external evaluation which uses a mixed‐method (quantitative/qualitative) approach to inform and evaluate change in five specific targeted areas identified for improvement: 

```{r Report, echo=echoChunks, message=TRUE, results='asis'}
```

<!--
# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
-->
