---
title: "Research Products: HRSA/ACF D89MC23154"
output:
  html_document:
    css: include/custom.css
---

***
***
# Overview

Project Duration: 2011-2015

> Evaluates MIECHV expansion and enhancement of Evidence-based Home Visitation programs in four Oklahoma counties.

This page contains the products from the 2011 funded proposal, [HRSA/ACF D89MC23154](https://perf-data.hrsa.gov/mchb/DGISReports/Abstract/AbstractDetails.aspx?Source=TVIS&GrantNo=D89MC23154&FY=2012): "OUHSC CCAN Independent Evaluation of the State of Oklahoma Competitive Maternal, Infant, and Early Childhood Home Visiting (MIECHV) Project." 

***
***
# Resources and Files
Understanding of this proposal may benefit from the following resources: 

 * [Protocol Description](./funding/2011a/HrsaProtocolV4.pdf)
 * [Expansion Program Logic Model](./funding/2011a/funding_2011a_logic_model.pdf)
 * [Home Visiting SWOT](./research/2011a/SWOT_Home_Visitation_ar_formatting_dbv2.pdf): White Paper Report on Home Visitation in Oklahoma, July 2013

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of just one directory.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
#   opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  fig.width = 6.5, 
  fig.height = 4, 
  fig.path = 'FigureRaw/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./research_2011a.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r LoadData, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r TweakData, echo=echoChunks, results='show', message=FALSE}
```

***
***
# Aims of the External Evaluation
#### Description
Oklahoma's Maternal, Infant, Early Childhood Home Visitation (MIECHV) Expansion project has two primary branches  of evaluation, the *internal* evaluation conducted by the Oklahoma State Dept. of Health (OSDH) and the *external* evaluation conducted by the OU Health Sciences Center, Center on Child Abuse and Neglect (CCAN).  This summary report describes the progress to date for the external evaluation which uses a mixed‐method (quantitative/qualitative) approach to inform and evaluate change in five specific targeted areas identified for improvement.

#### Impact
These five targeted aims of the evaluation intersect with all four of the national MIECHV areas of relevance.  The data obtained and evaluated will inform program planning and implementation (aims 1, 2, 3, 4, & 5), will evaluate effectiveness of planned strategies that are intended to enhance and sustain implementation (aims 1, 2, 3, & 5), will evaluate the capacity to support and monitor quality of scaled up evidence-based (EB) home visitation service continuum (aim 1), and will assess the effectiveness of home visitation on key outcomes that overlap with the national MIECHV benchmarks and constructs (aim 5).  

#### Reporting Strategy
The overall analysis is progressing from a set of general inquiries to a set of focused protocol subaims.  Our current reports do not map 1-to-1 to our protocol subaims.  Our intermediate reporting structure allows us to communicate better with stakeholders and other researchers (because the organization of issues can be different from their perspective).  The reports are currently structured so that we can approach others with a single document, instead of several scattered documents. Consequently, the following subaims are frequently addressed by several reports, and multiple subaims can refer to a common report.  By the conclusion of our external evaluation, each subaim will be addressed by a single, exclusive report.

We use a literate programming framework and code repository that facilitates agile and reproducible research.  We invite readers to view the analysis code and resulting documents housed in this [GitHub repository](https://github.com/OuhscCcanMiechvEvaluation/MReporting).  However, we ask that you not pass the GitHub  username and password to anyone who did not received it from us.  If you know someone who would like to review the repository, please have them contact [us](william-beasley@ouhsc.edu) and we likely will grant them permission. (Even with the username, no PHI is accessible from the repository; an authorized OUHSC user account is required.)

```{r Report, echo=echoChunks, message=TRUE, results='asis'}
```

***
***
# Collaborators and Stakeholders

 * [OUHSC Pediatrics](./about_collaborators.html#ouhsc-pediatrics)
 * [OSDH](./about_collaborators.html#osdh)
 * [OHCA](./about_collaborators.html#ohca)
 * [Smart Start Oklahoma](./about_collaborators.html#smart-start-oklahoma)

***
***
# Additional Information
 * For more information about the grant proposal, please see the project's 
[funding page](./funding_2011a.html).

<!--
# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
-->
