---
title: "Aim 1B -Oklaoma MIECHV"
output:
  html_document:
    theme: cerulean
    toc: true
---

## Goals
This report covers Aim 1B: 
**Develop timeline and analytic covariates that chronicle major program events**

 i.	Record successful establishment of a centralized referral/triage system
 ii. Assess frequency of home visitation coalition meetings
 iii.	Record the successful establishment of Connectors in each county
 iv. Record frequency of Connector initiated network meetings 
 v.	Record number of Memorandums of Agreement and/or Understanding between local services
 
For a complete list of the project's reports, see http://ouhscbbmc.github.io/MReportingPublic/research_2011a.html.


<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  dpi = 100,
  fig.width = 13, 
  fig.height = 25, 
  fig.path = 'FigureRaw/'
)
# 
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./Aim1/Aim1B/Aim1B.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r load_packages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare_globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r load_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak_data, echo=echoChunks, results='show', message=FALSE}
```

```{r convert_to_json, echo=echoChunks, results='show', message=FALSE}
```

```{r print_json, echo=echoChunks, results='asis'}
# cat("<!-- ")
# cat(json)
# cat(" -->")
```

## Timeline of Oklahoma's [MIECHV](http://www.ok.gov/health/Child_and_Family_Health/Family_Support_and_Prevention_Service/MIECHV_Program_-_Federal_Home_Visiting_Grant/MIECHV_Program_Resources/index.html) Progress

```{r timeline_ggplot, echo=echoChunks, message=TRUE}
```

The ascending-date table has the same information as the graphic above it, but its text is searchable and selectable.
```{r table, echo=echoChunks, message=TRUE, results='markup'}
```

# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
