---
title: "History of [MIECHV](http://www.ok.gov/health/Child_and_Family_Health/Family_Support_and_Prevention_Service/MIECHV_Program_-_Federal_Home_Visiting_Grant/MIECHV_Program_Resources/index.html) in Oklahoma"
output:
  html_document:
    theme: cerulean
    toc: true
    keep_md: true
    css: css/mreporting_style.css
---

*Background*: This report is part of [Oklahoma's External Evaluation of MIECHV](http://ouhscbbmc.github.io/MReportingPublic). "The Maternal, Infant, and Early Childhood Home Visiting project supports pregnant women and families and helps at-risk parents of children from birth to kindergarten entry tap the resources and hone the skills they need to raise children who are physically, socially and emotionally healthy and ready to learn" ([HRSA, 2015](http://mchb.hrsa.gov/programs/homevisiting/)). Oklahoma's current focus is to expand services and explore the effectiveness of different approaches.  For more details about the project, please see our [website](http://ouhscbbmc.github.io/MReportingPublic/) and [list of reports](http://ouhscbbmc.github.io/MReportingPublic/research_2011a.html).

## Goals

**Develop timeline and analytic covariates that chronicle major program events.**

 i.	Record successful establishment of a centralized referral/triage system
 ii. Assess frequency of home visitation coalition meetings
 iii.	Record the successful establishment of Connectors in each county
 iv. Record frequency of Connector initiated network meetings 
 v.	Record number of Memorandums of Agreement and/or Understanding between local services
 
<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())
  library(knitr)
  opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  dpi = 100,
  fig.width = 13, 
  fig.height = 25, 
  fig.path = 'FigureRaw/'
)
# 
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./Aim1/Aim1B/Aim1B.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r load_packages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare_globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r load_data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak_data, echo=echoChunks, results='show', message=FALSE}
```

## Interactive Timeline

<iframe src='https://cdn.knightlab.com/libs/timeline/latest/embed/index.html?source=1W378rcBIvRdFRIf5owQE0n_54phb7jZWD8P9V3i5TWI&font=Bevan-PotanoSans&maptype=toner&lang=en&start_zoom_adjust=-2&height=700' width='100%' height='700' frameborder='0'></iframe>


## Searchable Table
The ascending-date table has the same information as the graphic above it, but its text is more easily searchable and selectable.
```{r table, echo=echoChunks, message=TRUE, results='markup'}
```

# Session Information
For the sake of documentation and reproducibility, the current report was rendered on a system using the following software.  The dataset is available in either a [raw](https://raw.githubusercontent.com/OuhscBbmc/MReportingPublic/master/DataPhiFree/Raw/MiechvProgressTimeline.csv) or [tabled](https://github.com/OuhscBbmc/MReportingPublic/blob/master/DataPhiFree/Raw/MiechvProgressTimeline.csv) format on the project's [public repository](https://github.com/OuhscBbmc/MReportingPublic).  The interactive timeline uses [Timeline JS](http://timeline.knightlab.com/).  Thumbnails are captured and served by [PagePeeker](http://pagepeeker.com/about/).

```{r session_info, echo=FALSE}
cat("Report rendered by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
